NFC and burnout in teachers - A replication and extension study

### 2022-07-25 Manuscript/Revision_Letter.Rmd
responded to model fit in supplement

@@

>>>>

That is right, thank you for pointing it out.
We have added the fit measures of the replication of Grass et al. (2018) and of the demand-resource-ratio model without the outlier in the supplementary material below Table S2.2 and Table S2.3, respectively.

@@

That was an oversight on our part, we have added the degrees of freedom to the Chi Square test statistic.
